---
output:
  html_document:
    self_contained: FALSE
    theme: "paper"
---

# Tweetment {.tabset}

## Load data

```{r}
options(stringsAsFactors = F)
library(dplyr)

##choose which assumption--the conservative assumption file replicates the analysis in the appendix

standard <- read.csv(file = "data/data_anonymized_standard_assumption.csv")

conservative <- read.csv(file = "data/data_anonymized_conservative_assumption.csv")


##encode treatment varaible as a factor
standard$treatment = recode( standard$treat.f, "0" = "Control Group","1"= "In-Group/Low","2" = "Out-Group/Low","3" = "In-Group/High","4" = "Out-Group/High")
standard$treat.f <- as.factor(standard$treat.f)

conservative$treatment = recode( conservative$treat.f, "0" = "Control Group","1"= "In-Group/Low","2" = "Out-Group/Low","3" = "In-Group/High","4" = "Out-Group/High")
conservative$treat.f<-as.factor(conservative$treat.f)
```


## Standard assumption
```{r}
#1 week time period

##first model is the full analysis

(wk1_rac<-summary(lm(racism.scores.post.1wk ~ treat.f + log.followers +  racism.scores.pre.2mon, data = standard)))

##second model looks only at the most anonymous users

(wk1_rac_anon<-summary(lm(racism.scores.post.1wk ~ treat.f  + log.followers + racism.scores.pre.2mon,
                         data = filter(standard,anonymity>1) )))

##third model looks at non-anonymous users

(wk1_rac_id<-summary(lm(racism.scores.post.1wk ~ treat.f  + log.followers + racism.scores.pre.2mon,
                       data = filter(standard,anonymity<2))))



#2weeks


(wk2_rac<-summary(lm(racism.scores.post.2wk ~ treat.f+ log.followers +  racism.scores.pre.2mon, data = standard)))

(wk2_rac_anon<-summary(lm(racism.scores.post.2wk ~ treat.f  + log.followers + racism.scores.pre.2mon,
                         data = filter(standard,anonymity>1))))

(wk2_rac_id<-summary(lm(racism.scores.post.2wk ~ treat.f  + log.followers + racism.scores.pre.2mon,
                       data = filter(standard,anonymity<2))))


#1month

(mon1_rac<-summary(lm(racism.scores.post.1mon ~ treat.f  + log.followers + racism.scores.pre.2mon, data = standard)))

(mon1_rac_anon<-summary(lm(racism.scores.post.1mon ~ treat.f  + log.followers + racism.scores.pre.2mon,
                          data = filter(standard,anonymity>1))))

(mon1_rac_id<-summary(lm(racism.scores.post.1mon ~ treat.f  + log.followers + racism.scores.pre.2mon,
                        data = filter(standard,anonymity<2))))



#2 months
(mon2_rac<-summary(lm(racism.scores.post.2mon ~ treat.f  + log.followers +  racism.scores.pre.2mon, data = standard)))

(mon2_rac_anon<-summary(lm(racism.scores.post.2mon ~ treat.f  + log.followers + racism.scores.pre.2mon,
                          data = filter(standard,anonymity>1))))

(mon2_rac_id<-summary(lm(racism.scores.post.2mon ~ treat.f  + log.followers + racism.scores.pre.2mon,
                        data = filter(standard,anonymity<2))))
```

## Plot standard

```
#########################################################################;
#  File-Name: plot_results.R				                                    #;
#  Date: September 28, 2016				                                    	#;
#  Author:	KM							                                            #;
#  Purpose:	Plot results                                                #;
#########################################################################;
```

```{r}
#############################This is to run the models divided by anonymity models

models<-list(   wk2_rac_anon, wk2_rac_id, mon1_rac_anon, mon1_rac_id,  
              mon2_rac_anon, mon2_rac_id)

modelnames<-list(   "wk2_rac_anon", "wk2_rac_id", "mon1_rac_anon", "mon1_rac_id",  
                    "mon2_rac_anon", "mon2_rac_id")


##need to sepearate out the first ones to be the only ones that have labeled axes, for space
wk1_models<-list(wk1_rac_anon, wk1_rac_id)

wk1_modelnames<-list("wk1_rac_anon", "wk1_rac_id")



##############################This is to run the full models 

models<-list(   wk2_rac,  mon1_rac,  mon2_rac)
modelnames<-list(   "wk2_rac",   "mon1_rac",   "mon2_rac" )

##need to sepearate out the first ones to be the only ones that have labeled axes, for space

wk1_models<-list(wk1_rac)

wk1_modelnames<-list("wk1_rac")



##plot the wk1 models, with axis labels

for (i in 1:length(wk1_models)){
  ##change length, one fewer coefficient
  coefs <- t(t(c(wk1_models[[i]]$coefficients[2:6,1])))
  ses <- t(t(c(wk1_models[[i]]$coefficients[2:6,2])))
  y.axis <- c(1:5)
  #fix x axis to the max values any coefficients take for comparison
  min <- (-.65)
  max <- .55
  var.names <- c("In-Group/Low","Out-Group/Low","In-Group/High","Out-Group/High", "Log Followers")
  adjust <- 0
  ##########################
  ###change filename depending on the data source
  ##########################
  par(mar=c(4,6,1,1))
  
  plot(coefs[,1], y.axis, type = "p", axes = F, xlab = "Change in Average Daily Slur Use", ylab = "", pch = 19, cex = .8, 
       xlim=c(min,max),ylim = c(.5,5.5), main = "")
  rect(min,.5,max,1.5, col = c("grey97"), border="grey90", lty = 2)
  rect(min,1.5,max,2.5, col = c("grey95"), border="grey90", lty = 2)
  rect(min,2.5,max,3.5, col = c("grey97"), border="grey90", lty = 2)
  rect(min,3.5,max,4.5, col = c("grey95"), border="grey90", lty = 2)
  rect(min,4.5,max,5.5, col = c("grey97"), border="grey90", lty = 2)
  
  axis(1, tick = T,cex.axis = .75, mgp = c(2,.7,0))
  axis(2, at = y.axis, label = var.names, las = 1, tick = FALSE, cex.axis =.8, hadj=1)
  abline(h = y.axis, lty = 2, lwd = .5, col = "white")
  segments(coefs[,1]-qnorm(.975)*ses[,1], y.axis+2*adjust, coefs[,1]+qnorm(.975)*ses[,1], y.axis+2*adjust, lwd =  1)
  
  segments(coefs[,1]-qnorm(.95)*ses[,1], y.axis+2*adjust-.035, coefs[,1]-qnorm(.95)*ses[,1], y.axis+2*adjust+.035, lwd = .9)
  segments(coefs[,1]+qnorm(.95)*ses[,1], y.axis+2*adjust-.035, coefs[,1]+qnorm(.95)*ses[,1], y.axis+2*adjust+.035, lwd = .9)
  points(coefs[,1], y.axis+2*adjust,pch=21,cex=.8, bg="white")
  abline(v=0, lty = 2) # draw dotted line through 0 for reference line for null sign ificance hypothesis testing

}

##plot the other models, without axis labels

for (i in 1:length(models)){
  ##change length, one fewer coefficient
  coefs <- t(t(c(models[[i]]$coefficients[2:6,1])))
  ses <- t(t(c(models[[i]]$coefficients[2:6,2])))
  y.axis <- c(1:5)
  #fix x axis to the max values any coefficients take for comparison
  min <- (-.65)
  max <- .55
  #var.names <- c("In-group/Low Followers","Out-group/Low Followers","In-group/High Followers","Out-group/High Followers", "Log Followers")
  adjust <- 0
  ##########################
  ###change filename depending on the data source
  ##########################
  par(mar=c(4,1,1,1))
  
  plot(coefs[,1], y.axis, type = "p", axes = F, xlab = "", ylab = "", pch = 19, cex = .8, 
       xlim=c(min,max),ylim = c(.5,5.5), main = "")
  rect(min,.5,max,1.5, col = c("grey97"), border="grey90", lty = 2)
  rect(min,1.5,max,2.5, col = c("grey95"), border="grey90", lty = 2)
  rect(min,2.5,max,3.5, col = c("grey97"), border="grey90", lty = 2)
  rect(min,3.5,max,4.5, col = c("grey95"), border="grey90", lty = 2)
  rect(min,4.5,max,5.5, col = c("grey97"), border="grey90", lty = 2)
  ?axis
  axis(1, tick = T,cex.axis = .75, mgp = c(2,.7,0))
  #axis(2, at = y.axis, label = var.names, las = 1, tick = FALSE, cex.axis =.8, hadj=1)
  abline(h = y.axis, lty = 2, lwd = .5, col = "white")
  segments(coefs[,1]-qnorm(.975)*ses[,1], y.axis+2*adjust, coefs[,1]+qnorm(.975)*ses[,1], y.axis+2*adjust, lwd =  1)
  
  segments(coefs[,1]-qnorm(.95)*ses[,1], y.axis+2*adjust-.035, coefs[,1]-qnorm(.95)*ses[,1], y.axis+2*adjust+.035, lwd = .9)
  segments(coefs[,1]+qnorm(.95)*ses[,1], y.axis+2*adjust-.035, coefs[,1]+qnorm(.95)*ses[,1], y.axis+2*adjust+.035, lwd = .9)
  points(coefs[,1], y.axis+2*adjust,pch=21,cex=.8, bg="white")
  abline(v=0, lty = 2) # draw dotted line through 0 for reference line for null sign ificance hypothesis testing

}
```


## Conservative assumption

```{r}
#1 week time period

##first model is the full analysis

(wk1_rac<-summary(lm(racism.scores.post.1wk ~ treat.f + log.followers +  racism.scores.pre.2mon, data = conservative)))

##second model looks only at the most anonymous users

(wk1_rac_anon<-summary(lm(racism.scores.post.1wk ~ treat.f  + log.followers + racism.scores.pre.2mon,
												 data = filter(conservative,anonymity>1) )))

##third model looks at non-anonymous users

(wk1_rac_id<-summary(lm(racism.scores.post.1wk ~ treat.f  + log.followers + racism.scores.pre.2mon,
											 data = filter(conservative,anonymity<2))))



#2weeks


(wk2_rac<-summary(lm(racism.scores.post.2wk ~ treat.f+ log.followers +  racism.scores.pre.2mon, data = conservative)))

(wk2_rac_anon<-summary(lm(racism.scores.post.2wk ~ treat.f  + log.followers + racism.scores.pre.2mon,
												 data = filter(conservative,anonymity>1))))

(wk2_rac_id<-summary(lm(racism.scores.post.2wk ~ treat.f  + log.followers + racism.scores.pre.2mon,
											 data = filter(conservative,anonymity<2))))


#1month

(mon1_rac<-summary(lm(racism.scores.post.1mon ~ treat.f  + log.followers + racism.scores.pre.2mon, data = conservative)))

(mon1_rac_anon<-summary(lm(racism.scores.post.1mon ~ treat.f  + log.followers + racism.scores.pre.2mon,
													data = filter(conservative,anonymity>1))))

(mon1_rac_id<-summary(lm(racism.scores.post.1mon ~ treat.f  + log.followers + racism.scores.pre.2mon,
												data = filter(conservative,anonymity<2))))





#2 months
(mon2_rac<-summary(lm(racism.scores.post.2mon ~ treat.f  + log.followers +  racism.scores.pre.2mon, data = conservative)))

(mon2_rac_anon<-summary(lm(racism.scores.post.2mon ~ treat.f  + log.followers + racism.scores.pre.2mon,
													data = filter(conservative,anonymity>1))))

(mon2_rac_id<-summary(lm(racism.scores.post.2mon ~ treat.f  + log.followers + racism.scores.pre.2mon,
												data = filter(conservative,anonymity<2))))
```


## Plot Conservative

```{r}
{
  ##change length, one fewer coefficient
  coefs <- t(t(c(models[[i]]$coefficients[2:6,1])))
  ses <- t(t(c(models[[i]]$coefficients[2:6,2])))
  y.axis <- c(1:5)
  #fix x axis to the max values any coefficients take for comparison
  min <- (-.65)
  max <- .55
  #var.names <- c("In-group/Low Followers","Out-group/Low Followers","In-group/High Followers","Out-group/High Followers", "Log Followers")
  adjust <- 0
  ##########################
  ###change filename depending on the data source
  ##########################
  par(mar=c(4,1,1,1))
  
  plot(coefs[,1], y.axis, type = "p", axes = F, xlab = "", ylab = "", pch = 19, cex = .8, 
       xlim=c(min,max),ylim = c(.5,5.5), main = "")
  rect(min,.5,max,1.5, col = c("grey97"), border="grey90", lty = 2)
  rect(min,1.5,max,2.5, col = c("grey95"), border="grey90", lty = 2)
  rect(min,2.5,max,3.5, col = c("grey97"), border="grey90", lty = 2)
  rect(min,3.5,max,4.5, col = c("grey95"), border="grey90", lty = 2)
  rect(min,4.5,max,5.5, col = c("grey97"), border="grey90", lty = 2)
  ?axis
  axis(1, tick = T,cex.axis = .75, mgp = c(2,.7,0))
  #axis(2, at = y.axis, label = var.names, las = 1, tick = FALSE, cex.axis =.8, hadj=1)
  abline(h = y.axis, lty = 2, lwd = .5, col = "white")
  segments(coefs[,1]-qnorm(.975)*ses[,1], y.axis+2*adjust, coefs[,1]+qnorm(.975)*ses[,1], y.axis+2*adjust, lwd =  1)
  
  segments(coefs[,1]-qnorm(.95)*ses[,1], y.axis+2*adjust-.035, coefs[,1]-qnorm(.95)*ses[,1], y.axis+2*adjust+.035, lwd = .9)
  segments(coefs[,1]+qnorm(.95)*ses[,1], y.axis+2*adjust-.035, coefs[,1]+qnorm(.95)*ses[,1], y.axis+2*adjust+.035, lwd = .9)
  points(coefs[,1], y.axis+2*adjust,pch=21,cex=.8, bg="white")
  abline(v=0, lty = 2) # draw dotted line through 0 for reference line for null sign ificance hypothesis testing

}
```


## Robustness analysis {.tabset}
Using Bayesian regression modelling and a Poisson distribution.

### Get counts
Reproduce full analysis with a different distribution for the outcome (Poisson instead normal)

```{r}
library(ggplot2)
standard$anonymity = factor(standard$anonymity)
qplot(standard$racism.scores.post.1wk) # looks like Poisson or zero-inflated Poisson
library(brms)
standard$racism.counts.post.1wk = round(standard$racism.scores.post.1wk * 7)
standard$racism.counts.post.2wk = round(standard$racism.scores.post.2wk * 14)
standard$racism.counts.post.1mon = round(standard$racism.scores.post.1mon * 31)
standard$racism.counts.post.2mon = round(standard$racism.scores.post.2mon * 62)
table(standard$racism.counts.post.1wk <= standard$racism.counts.post.2wk)
qplot(standard$racism.counts.post.1mon, standard$racism.counts.post.1wk)

standard$racism.counts.post.2wk_inclusive = standard$racism.counts.post.2wk
standard$racism.counts.post.2wk = standard$racism.counts.post.2wk - standard$racism.counts.post.1wk
```

### Week 1

```{r}
(wk1_rac <- brm(racism.counts.post.1wk ~ treatment + log.followers +  racism.scores.pre.2mon, data = standard, family = poisson))

summary(wk1_rac)

marginal_effects(wk1_rac)

standard$racism.counts.post.2mon = round(standard$racism.scores.post.2mon * 30)
```

### Week 2 - Month 2

Does the effect last? 
We have to subtract the counts from the first week so as not to do pseudo-replication.
```{r}
(wk2i_rac <- brm(racism.counts.post.2wk_inclusive ~ treatment + log.followers +  racism.scores.pre.2mon, data = standard, family = poisson))
marginal_effects(wk2i_rac)

(wk2_rac <- brm(racism.counts.post.2wk ~ treatment + log.followers +  racism.scores.pre.2mon, data = standard, family = poisson))
marginal_effects(wk2_rac)
```

```{r}
standard$racism.counts.post.1mon = standard$racism.counts.post.1mon - standard$racism.counts.post.2wk
(mon1_rac <- brm(racism.counts.post.1mon ~ treatment + log.followers +  racism.scores.pre.2mon, data = standard, family = poisson))
summary(mon1_rac)
marginal_effects(mon1_rac)
```
```{r}
(mon2_rac <- brm(racism.counts.post.2mon ~ treatment + log.followers +  racism.scores.pre.2mon, data = standard, family = poisson))
summary(mon2_rac)
marginal_effects(mon2_rac)
```

```{r}
(mon2_racanon <- brm(racism.counts.post.2mon ~ anonymity * treatment + log.followers +  racism.scores.pre.2mon, data = standard, family = poisson))
summary(mon2_racanon)
marginal_effects(mon2_racanon)
```

### go back in time

Let's see whether the groups differed at the outset. Yes, some outliers, good to control for this heterogeneity.

```{r}
standard$racism.counts.pre.2mon = round(standard$racism.scores.pre.2mon * 62)
(backwards_2m <- brm(racism.counts.pre.2mon ~ treatment + log.followers, data = standard, family = poisson))
summary(backwards_2m)
marginal_effects(backwards_2m)
library(ggforce)
ggplot(aes(treatment, racism.counts.pre.2mon), data = standard) + geom_sina()
ggplot(aes(treatment, racism.counts.post.2mon), data = standard) + geom_sina() + scale_y_log10() + geom_pointrange(stat ="summary", fun.data = "mean_cl_boot")
ggplot(aes(treatment, racism.counts.pre.2mon), data = standard) + geom_sina() + geom_pointrange(stat ="summary", fun.data = "mean_cl_boot", color = "red")
ggplot(aes(treatment, racism.counts.post.2mon), data = standard) + geom_sina() + geom_pointrange(stat ="summary", fun.data = "mean_cl_boot", color = "red")
```


### Graph the effect
```{r}
ggplot(aes(racism.counts.pre.2mon, racism.counts.post.2mon), data = standard) + geom_jitter() + coord_cartesian(ylim = c(0,50), xlim = c(0, 50)) + geom_smooth(method = "lm")

ggplot(aes(racism.counts.pre.2mon, racism.counts.post.2mon, colour = treatment), data = standard) + geom_jitter() + coord_cartesian(ylim = c(0,50), xlim = c(0, 50)) + geom_smooth(method = "lm")
```


### Interaction by level
Are very active tweeters discouraged more/less?

```{r}
(mon2_rac_interact_with_pre <- brm(racism.counts.post.2mon ~ racism.scores.pre.2mon * treatment + log.followers, data = standard, family = poisson))
summary(mon2_rac_interact_with_pre)
```

